\textsc{Rils}-\textsc{Rols} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-13 paper_resources/doc/paper.tex
CD plots: description updated

Initially, Friedman’s test was separately executed for all competitor approaches.      In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained results of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}. The outcome is represented by means of critical difference (CD) plots. In each CD plot, the (15) competitor approaches are placed on the horizontal axis according to their average ranking. Thereafter, the CD score is computed for a significance level of 0.05. If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is drawn.   The corresponding three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts}. The following conclusions may be drawn from there. \fxnote{Marko: update text}

\begin{itemize}
	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method returns the best average ranking in terms of   exact percentage rate.  The second best ranking is achieved by \textsc{AI-Feynman} algorithm. There is no statistically significant difference between these two approaches w.r.t.\ obtained exact percentages. However, these two approaches perform statistically significantly better than the third best approach according the the average raking, \textsc{Apf-Fe}. This conclusion also holds for the remaining approaches, which are performing statistically significantly worse than  \textsc{Rils}-\textsc{Rols} method. 
	\item    Concerning the instance problems with the  level of noise equal to 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the exact percentage rate.   The second best ranking is achieved by \textsc{AI-Feynman} algorithm. However,  there is no statistically significant difference between these two approaches. The third best approach is \textsc{Afp-Fe} which perform statistically equal to \textsc{Afp} and \textsc{AI-Feynman}, but statistically significantly worse than our \textsc{Rils}-\textsc{Rols} method. For all remaining approaches,  \textsc{Rils}--\textsc{Rols} performs statistically better in terms of obtained exact percentages.
	\item  Concerning the instance problems with the noise level of  0.01, again, \textsc{Rils-Rols} produces the best average ranking according to obtained exact percentages; the second best approach is \textsc{Afp-Fe} and \textsc{Afp}. These latter three approaches perform statistically equal. 
	The fourth best approach according to its average ranking is \textsc{AI-Feynman} which is tied to \textsc{gplearn}. The the exact percentages obtained by the latter two approaches are statistically worse than those of the \textsc{Rils}--\textsc{Rols} method.  This also holds when \textsc{Rils-Rols} is compared to all   remaining approaches.

>>>>

Initially, Friedman’s test was separately executed for all competitor approaches.      In those cases in which the null hypothesis $H_0$ was rejected ($H_0$ states that there are no statistical differences between the obtained results of all competitors) pairwise comparisons are further performed by using the Nemenyi post-hoc test~\cite{pohlert2014pairwise}. The outcome is represented by means of critical difference (CD) plots. In each CD plot, the (15) competitor approaches are placed on the horizontal axis according to their average ranking. Thereafter, the CD score is computed for a significance level of 0.05. If the difference is small enough, meaning that no statistical difference is detected, a horizontal bar linking statistically equal approaches is drawn.   The corresponding three (one for each level of noise) CD plots are shown in Figure~\ref{fig:cd-plots-exact-pcts}. The following conclusions may be drawn from there.

\begin{itemize}
	\item  Concerning the instance problems where no noise is included, \textsc{Rils}-\textsc{Rols} method returns the best average ranking in terms of obtained exact models.  The second best average ranking is achieved by \textsc{AI-Feynman} algorithm. There is  statistically significant difference between these two approaches w.r.t.\ number of found exact models. The third best approach is \textsc{Apf-Fe},  which is far behind \textsc{Rils}-\textsc{Rols} w.r.t.\ delivered average raking.  
	\item    Concerning the instance problems with the  level of noise equal to 0.001, \textsc{Rils}-\textsc{Rols} method again obtains the best average ranking in terms of the found exact models.   The second best ranking is obtained by \textsc{AI-Feynman} algorithm. There is again a statistically significant difference between the results obtained by these two approaches. The third best approach is \textsc{Afp-Fe} which perform statistically worse from \textsc{AI-Feynman}.  
	\item  Concerning the instance problems with the noise level of  0.01, again, \textsc{Rils-Rols} method produces the best average ranking according to obtained exact models; the second best approach w.r.t.\ average ranking is \textsc{Afp-Fe}, followed by \text{Dsr}, and \textsc{Afp}. These latter three approaches perform statistically equal, but significantly worse than \text{Rils}-\textsc{Rols} method. 	The fourth best approach according to its average ranking is \textsc{AI-Feynman} which is on pair with \textsc{gplearn}. Note that the average ranking of \textsc{AI-Feynman} method declines by increasing  the level of noise in the input data. Thus, despite being efficient on no-noisy data, it seem that \textsc{AI-Feynman} is very sensitive to the noise, which is not that dramatically conspicuous with our \textsc{Rils}-\textsc{Rols} method.

	 \fxnote{Marko: update text}
\end{itemize}
